Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-06 paper/paper.tex
add new reference

There has been previous work to formally verify uncertain linear systems stability 
in digital controllers with considerations to the implementation aspects~\cite{Bessa16}.
In particular, Bessa {\it et al.} considers finite-word length
(FWL) effects over controllers and also parameter uncertainties
in the context of verifying the (so-called) robust non-fragile stability.
However, the authors do not consider the compete range of approximations, 
related to time discretisation, and quantisation effects. Additionally, they do not find 
a parametric solution for a digital controller given a continuous plant specification, 
in order to synthesize the controller implementation.

@@

Since the digital control synthesis is performed over a hybrid model,
where the plant displays a continuous behaviour and the controller
operates in both discrete time and state-space, we initially translate
the problem into a single domain which represents a bi-simulation of
the original dynamics. Given our primary interest in evaluating digital
effects in addition to stability, we have modeled a digital equivalent
of the plant by evaluating the effects of the quantisers (A/D and D/A
converters) as time discretisation elements with quantisation noise.
The resulting closed loop system is a program loop working over
bit-vectors of fixed point arithmetic with fixed word length. The
effect of the FWL is included in the model as a parametric uncertainty
which must be taken into account for the correct synthesis of the
controller.

>>>>

There has been previous work to formally verify uncertain linear systems stability 
in digital controllers with considerations to the implementation aspects~\cite{Bessa16}.
In particular, Bessa {\it et al.} considers finite-word length
(FWL) effects over controllers and also parameter uncertainties
in the context of verifying the (so-called) robust non-fragile stability~\cite{bhattacharyya97}.
However, the authors do not consider the compete range of approximations, 
related to time discretisation, and quantisation effects. As a result,
the stability verification method proposed by Bessa {\it et al.} is incomplete, 
given that false alarms can be produced due to the quantisation effects. 
Additionally, the authors do not find a parametric solution for a digital controller 
given a continuous plant specification, in order to synthesize the controller implementation.

@@

Since the digital control synthesis is performed over a hybrid model,
where the plant displays a continuous behaviour and the controller
operates in both discrete time and state-space, we initially translate
the problem into a single domain which represents a bi-simulation of
the original dynamics. Given our primary interest in evaluating digital
effects in addition to stability, we have modeled a digital equivalent
of the plant by evaluating the effects of the quantisers (A/D and D/A
converters) as time discretisation elements with quantisation noise.
The resulting closed loop system is a program loop working over
bit-vectors of fixed-point arithmetic with fixed word length. The
effect of the FWL is included in the model as a parametric uncertainty
which must be taken into account for the correct synthesis of the
controller.
